%----------------------------------------------------------------------------------------
%
% Version en anglais
% À mettre à jour régulièrement EN MÊME TEMPS que la version en français (au fur et à mesure, si possible).
%
% - Adrien
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	Packages et configuration 
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{soul}
\usepackage[scale=0.75]{geometry} % Reduce document margins
\usepackage{lastpage}
\usepackage{fancyhdr}
\fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}

\pagestyle{fancy}

%----------------------------------------------------------------------------------------
%	Nom et info
%----------------------------------------------------------------------------------------

\firstname{Adrien} % Your first name
\familyname{Cloutier} % Your last name

\title{}
\address{Candidate to the Master of Political Science}{}
\mobile{Phone: (418) 590-2605}
\email{Email: adrien.cloutier.1@ulaval.ca}

\begin{document}

\makecvtitle

%----------------------------------------------------------------------------------------
%	Formation
%----------------------------------------------------------------------------------------

\section{\textbf{Education}}

\cvitem{2018 -- 2020}{\textbf{Université Laval}, Québec}
\cvitem{}{\textbf{Candidate to the Master of Political Science}, Director: \textit{Yannick Dufresne, Ph.D.}}
\cvitem{}{\textit{Interests}: Political communication; Public opinion; Journalism.}
\vspace{1em}

\cvitem{2019}{\textbf{University of Michigan}, Michigan}
\cvitem{}{\textbf{Summer Program in Quantitative Methods of Social Research}}
\cvitem{}{Inter-university Consortium for Political and Social Research (ICPSR)}
\vspace{1em}

\cvitem{2015 -- 2018}{\textbf{Université Laval}, Québec}
\cvitem{}{\textbf{Baccalaureate in Political Science}}
\vspace{1em}

\cvitem{2012 -- 2015}{\textbf{Cégep de Jonquière}, Jonquière}
\cvitem{}{\textbf{Technical in Art and Media Technology (ATM)}}
\cvitem{}{Journalism}
\vspace{1em}

\cvitem{2016}{\textbf{University of British Columbia (UBC)}, Vancouver}
\cvitem{}{\textbf{\textit{Explore} Intensive English-immersion program}}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\section{\textbf{Publications}}

\cvitem{2019}{\textbf{CLOUTIER, Adrien and Eric Montigny} \textit{As the push for provincial autonomy spreads, where will it lead?} Policy Options.}
\vspace{1em}

\section{\textbf{Publications in Writing}}

\cvitem{À venir}{BIBEAU, Alexis, \textbf{CLOUTIER, Adrien}, FRÉCHET, Nadjim, FORTIER-CHOUINARD, Alexandre and Camille TREMBLAY-ANTOINE. \textit{Covid-19 in the Media: A Comparative Analysis of Government Communication in Times of Crisis.} Université Laval.}
\vspace{1em}

\cvitem{In progress}{TOMKINSON, Sule and \textbf{Adrien CLOUTIER}. \textit{Managing the “Crisis” of Irregular Border Crossings: Media Narratives and Policy Responses in Canada.}. Université Laval.}
\vspace{1em}

\cvitem{In progress}{\textbf{CLOUTIER, Adrien}, DUFRESNE, Yannick, FRÉCHET, Nadjim and Camille TREMBLAY-ANTOINE. \textit{Cannabis, Alcohol and Tobacco. A Scoping Review on the “High” and “Down” of Canadian Public Opinion.} Université Laval.}
\vspace{1em}

\cvitem{In progress}{\textbf{CLOUTIER, Adrien} and Yannick DUFRESNE \textit{It’s Time to Weed Out: an Automated Media Analysis to Unveil Canadian Public Opinion on Cannabis.} Université Laval.}
\vspace{1em}

\cvitem{In progress}{DUFRESNE, Yannick, HOULE, David and \textbf{Adrien CLOUTIER}. \textit{Four Shades of Green : The Muldimentionality of Environmentalism and the Bases of its Support}. Université Laval, University of Michigan.}
\vspace{1em}

%----------------------------------------------------------------------------------------
% Conférences
%----------------------------------------------------------------------------------------

\section{\textbf{Conferences}}

\cvitem{2020}{Southern Political Science Association (SPSA) conference. \textit{Cannabis, Alcohol and Tobacco: A Scoping Review of the “High” and “Down” of Canadian Public Opinion.} San Juan, Puerto Rico.}
\vspace{1em}

\cvitem{2019}{The Canadian Political Science Association (CPSA) conference. \textit{Managing the “Crisis” of Irregular Border Crossings: Media Narratives and Policy Responses in Canada}. University of British Columbia (UBC), Vancouver.}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	Contrats
%----------------------------------------------------------------------------------------

\section{\textbf{Research Contracts}}

\cventry{2020}{Leadership Chair in the Teaching of Digital Social Science (CLESSN)}{Université Laval}{Québec}{Development of the RADAR+ Tool}
{Student reseacher with Pr. Yannick Dufresne and Pr. Lisa Burch.}
\vspace{1em}

\cventry{2019}{Leadership Chair in the Teaching of Digital Social Science (CLESSN)}{Université Laval}{Québec}{Research on Quebeckers' Perceptions of Alcohol}
{Student reseacher for the Institut nationale de santé publique du Québec (INSPQ).}
\vspace{1em}

\cventry{2018 -- 2019}{Department of Political Science}{Université Laval}{Québec}{Research on content analysis methods using crowdsourcing}
{Student reseacher with Pr. Yannick Dufresne and Pr. Mathieu Ouimet.}
\vspace{1em}

\cventry{2018 -- 2019}{Department of Political Science}{Université Laval}{Québec}{Scoping review regarding social acceptability of drug, tobacco and alcohol use}
{Student reseacher with Pr. Yannick Dufresne.}
\vspace{1em}

\cventry{2018}{Department of Political Science}{Université Laval}{Québec}{Construction of a Textbook for the Quantitative Analysis Course (POL-7004)}
{Student reseacher with Pr. Yannick Dufresne.}
\vspace{1em}

\cventry{2016 -- 2018}{Department of Political Science}{Université Laval}{Québec}{}
{Research Assistant for Pr. Sule Tomkinson.}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	Activité supplémentaires
%----------------------------------------------------------------------------------------

\section{\textbf{Extra-Curricular Activities}}

\cvitem{2020}{\textbf{Course Assistant}}
\cvitem{}{\textit{Analyse Quantitative (POL-7004).}}
\vspace{1em}

\cvitem{2019}{\textbf{Course Assistant}}
\cvitem{}{\textit{Persuasion sociale, influence et opinion publique (POL-2425).}}
\vspace{1em}

\cvitem{2019}{\textbf{National Public Administration Student Case Competition}}
\cvitem{}{\textit{Canadian Association of Programs in Public Policy (CAPPA).}}
\vspace{1em}

\cvitem{Since 2018}{\textbf{Volunteer journalist}}
\cvitem{}{\textit{Magazine de rue La Quête.}}
\vspace{1em}

\cvitem{2018}{\textbf{Researcher}}
\cvitem{}{\textit{Segma Recherche.}}
\vspace{1em}

\cvitem{2018}{\textbf{Researcher}}
\cvitem{}{\textit{2018 Electoral Compass}, Voxpop Labs.}
\vspace{1em}

\cvitem{2015 -- 2017}{\textbf{Journalist}}
\cvitem{}{\textit{Québec Hebdo}, TC Transcontinental.}
\vspace{1em}

\cvitem{2015}{\textbf{Internship in journalism}}
\cvitem{}{\textit{The Canadian Press at the National Assembly of Québec.}}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	 Groupe de recherche
%----------------------------------------------------------------------------------------

\section{\textbf{Research Groups}}

\cventry{2019 -- 2020}{Member of the Observatoire international sur les impacts sociétaux de l'IA et du numérique (OBVIA)}{Université Laval}{Québec}{}
{Student reseacher.}
\vspace{1em}

\cventry{2019 -- 2020}{Member of the Leadership Chair in the Teaching of Digital Social Science (CLESSN)}{Université Laval}{Québec}{}
{Student reseacher.}
\vspace{1em}

\cventry{2019 -- 2020}{Member of the Centre d'analyse des politiques publiques (CAPP)}{Université Laval}{Québec}{}
{Student reseacher.}
\vspace{1em}

\cventry{2018 -- 2020}{Member of the Political Communication Research Group}{Université Laval}{Québec}{}
{Student reseacher.}
\vspace{1em}

\cventry{2018 -- 2020}{Member of the Centre for the Study of Democratic Citizenship}{Université Laval}{Québec}{}
{Student reseacher.}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	Bourses et prix
%----------------------------------------------------------------------------------------

\section{\textbf{Scholarship and Grants}}

\cventry{2020}{methodological development Scholarship}{Leadership Chair in the Teaching of Digital Social Science}{Université Laval}{}
{}

\cventry{2019}{Methodology Training Scholarship}{Centre for the Study of Democratic Citizenship}{McGill University}{}
{}

\cventry{2019}{Methodology Training Scholarship}{Political Communication Research Group}{Université Laval}{}
{}

\cventry{2019}{Training Award in Qualitative or Quantitative Methods}{Department of Political Science}{Université Laval}{}
{}

\cventry{2019}{R Training Scholarship}{Department of Political Science}{Université Laval}{}
{}

\cventry{2018}{Merit Scholarship}{Chair in Digital Social Sciences Teaching Leadership}{Université Laval}{}
{}

\cventry{2017}{Dean's Honorary Mention}{Faculty of Social Sciences}{Université Laval}{}
{Rewards the excellence of academic results.}

\cventry{2016}{\textit{Explore} Program Scholarship}{Ministry of Higher Education}{Government of Québec}{Québec}
{}

\vspace{1em}

%----------------------------------------------------------------------------------------
%	Skillsssss
%----------------------------------------------------------------------------------------

\section{\textbf{Personal Skills}}

\cvitem{Programs}{LateX and Markdown languages, R Informatic language, HTML, Git, Vim, Adobe Suite, Microsoft office series.}
\vspace{1em}

\cvitem{Specialization}{Automated Text Analysis (Bag of Words, Topic Modeling.}
\vspace{1em}

\cvitem{Languages}{French and English.}
\vspace{1em}

%----------------------------------------------------------------------------------------
%	Références
%----------------------------------------------------------------------------------------

% \section{\textbf{Credentials}}

% Supplied on request.

\end{document}